SDSS-IV MaNGA: The Radial Profile of Enhanced Star Formation in Close Galaxy Pairs

### 2020-10-22 maintex.tex
shortened paragraphs in Sec 4.1.2

\subsubsection{Tailored-Controls Difference Profiles}\label{sec:tailored}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=\linewidth]{fig/ssfr_dm.pdf}
\caption[]{Same as Figure \ref{fig:ssfr_mass} except the difference profiles are split by mass ratio. The inside-IFU sample is left out of this analysis as their mass ratios are unreliable.}
\label{fig:ssfr_dm}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In the second method, we match each paired galaxy to a set of 20 control galaxies of similar stellar masses and redshifts, as described in Section \ref{sec:control}. We take the individual azimuthally averaged profiles of the selected control galaxies and take the median value of the profiles at each radius bin to produce the median profile of the control galaxies.

Once the median profile of the control galaxies is made, we take the difference between the paired galaxy's profile and the median control profile in log space. We do this process for each of the 175 paired galaxies.

The difference profiles at this stage have now been controlled for both stellar mass and redshift. We can freely stack these difference profiles to study their dependence on other parameter like the mass ratio and projected separation.

First, we split the profiles by stellar mass to see how this method compares to the previous mass-binning method. We split the individual difference profiles into five evenly spaced stellar mass bins between \logm\ $=$ 9.0$-$11.5 and stack the difference profiles within each mass bin. This gives us five difference profiles covering five different stellar mass ranges shown in the left hand panel of Figure \ref{fig:ssfr_mass}. The errors of the stacked profiles are the standard error of the mean of the difference profiles within each bin.

To focus on the sSFR offsets in the centers of the galaxies, we take the median sSFR within 0.5 \reff\ for all galaxies. We then calculate the offsets in the centers of the pairs by taking the difference between the sSFR in the centers of the pairs and the median sSFR of their 20 controls. We depict the central $\Delta$log(sSFR) as a function of stellar mass in the right hand panel of Figure \ref{fig:ssfr_mass}

@@

The results we obtain from the tailored-control method is largely consistent with the mass-binning method. Between the two methods we see that the $\Delta$log(sSFR) profile is independent of the total stellar mass of the galaxies. In the next two sections, we will use the tailored-control method to study how the profiles behave as a function of the mass ratio (Section \ref{sec:dm}) and projected separation (Section \ref{sec:sep}).

>>>>

\subsubsection{Tailored-Controls Difference Profiles}\label{sec:tailored}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=\linewidth]{fig/ssfr_dm.pdf}
\caption[]{Same as Figure \ref{fig:ssfr_mass} except the difference profiles are split by mass ratio. The inside-IFU sample is left out of this analysis as their mass ratios are unreliable.}
\label{fig:ssfr_dm}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In the second method, we match each paired galaxy to a set of 20 control galaxies of similar stellar masses and redshifts, as described in Section \ref{sec:control}. We then take the median of the azimuthally averaged profiles of the tailored control sample. Finally, we obtain the $\Delta\log$sSFR profile for each of the 175 paired galaxies by calculating the difference between its sSFR profile and the median profile of its control sample.

Before delving into merger parameters, we decided to stack the profiles by stellar mass to see how this method compares to the previous mass-binning method. We split the individual difference profiles into five evenly spaced stellar mass bins between \logm\ $=$ 9.0$-$11.5 and stack the difference profiles within each mass bin. This gives us five difference profiles covering five different stellar mass ranges shown in the left hand panel of Figure \ref{fig:ssfr_mass}. The errors of the stacked profiles are the standard error of the mean of the difference profiles within each bin.

To focus on the sSFR offsets in the centers of the galaxies, we also calculate the sSFR difference between each paired galaxy and its control sample in the central 0.5~\reff. We depict the central $\Delta$log(sSFR) as a function of stellar mass in the right hand panel of Figure \ref{fig:ssfr_mass}.

@@

The results we obtain from the tailored-control method is largely consistent with the mass-binning method. Between the two methods we see that the $\Delta$log(sSFR) profile is independent of the total stellar mass of the galaxies. In the next two sections, we will use the tailored-control method to study how the difference profiles behave as a function of the mass ratio (Section \ref{sec:dm}) and projected separation (Section \ref{sec:sep}).
